\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-11-25 tex/paper.tex
Aligned text and started writing about snapshots

Copy-on-Write is used in virtual memory management systems~\cite{VIRTCOW}, snapshot functionality in both file 
systems~\cite{BTRFS} and logical volume management systems~\cite{LVMCOW}, and as an optimisation technique for objects and 
types in programming languages\cite{LANGCOW}.

@@

\newpage 
\section{Copy-on-Write}
\label{sec:copy-on-write}
As the persistent storage does not implement transactions or locks a lot of different problems can occur when several 
clients are working on the same data set at the same time. Such problems could be race conditions and determining the 
happened-before relation. In this work this problem is solved by implementing Copy-on-Write.

@@

The front-end is written in ES6 with React and Reflux, the styling is done with the help of
Bootstrap.

@@

\subsection{Resulting system}
\subsubsection{Persistent storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its internal storage 
format called BSON, which is very similar to JSON which the API is using. As the formats are similar, the process of 
marshalling and unmarshalling becomes quite easy between the core code, MongoDB instance and REST interface. 
The second reason was that if the system needs to scale in the future it is very easy to distribute MongoDB and if 
needed the system can easily be migrated to Reactive Mongo, which is an asynchronous and 
non-blocking driver for MongoDB and can therefore make the system scale even further~\cite{REACTIVEMONGO}.

>>>>

Copy-on-Write is used in virtual memory management systems~\cite{VIRTCOW}, for snapshot
functionality in both file systems~\cite{BTRFS} and logical volume management systems~\cite{LVMCOW},
and as an optimisation technique for objects and types in programming languages\cite{LANGCOW}.

@@

\newpage 
\section{Snapshots}
Write what snapshots are
\subsection{Copy-on-Write}
\label{sec:copy-on-write}
To efficiently create snapshots of a system Copy-on-Write can be used to make it possible to create
snapshots in O(1)\cite{BTRFS}, this is due to the fact that to create a snapshot in a system using
Copy-on-Write you only need to reference the current nodes in the tree and make sure that they are
not removed, see Figure~\ref{fig:btrfs_tree}.

As the persistent storage, used in this implementation (Section~\ref{persistent_storage}), does not
implement transactions or locks a lot of different problems can occur when several clients are
working on the same data set at the same time. Such problems could be race conditions and
determining the happened-before relation. In this work this problem is solved by implementing
Copy-on-Write.

\subsection{Full Copy}

@@

The front-end is written in ES6 with React and Reflux, and the styling is done with the help of
Bootstrap.

@@

\subsection{Resulting system}
\subsubsection{Persistent storage}
\label{persistent_storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its
internal storage format called BSON, which is very similar to JSON which the API is using. As the
formats are similar, the process of marshalling and unmarshalling becomes quite easy between the
core code, MongoDB instance and REST interface.  The second reason was that if the system needs to
scale in the future it is very easy to distribute MongoDB and if needed the system can easily be
migrated to Reactive Mongo, which is an asynchronous and non-blocking driver for MongoDB and can
therefore make the system scale even further~\cite{REACTIVEMONGO}.
